Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-01-11 paperIEEE.tex
Conclusion
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@73 db7c848b-7755-4df2-b763-8796797afa52

In 2009 we presented the initial \textsf{Equalizer} parallel rendering
framework~\cite{EMP:09}, which introduced the architecture of a generic parallel
rendering framework and summarized the work in parallel rendering. Since then,
an extensive Programming and User Guide provides in-depth documentation on using
and programming \textsf{Equalizer}~\cite{Eilemann:13}. In the following related
work we assume these two publications and their references as a starting point,
and focus on the new work published since 2009.

@@

We have presented a significantly improved generic parallel rendering system
over the original publication \cite{EMP:09}. While the original publication
motivated the system design, this publication describes a feature-rich, mature
implementation capable of supporting a wide variety of use cases. We doubled the
support for scalable rendering modes, many of which presented for the first
time. We present new runtime adaptations for better load balance and
performance, describe how common optimizations are integrated into the system,
making Equalizer the most generically available scalable rendering system.

@@

RDMA needs further investigation.

>>>>

In 2009 we presented \textsf{Equalizer}~\cite{EMP:09}, which introduced the
architecture of a generic parallel rendering framework and summarized our work
in parallel rendering. Since then, an extensive Programming and User Guide
provides in-depth documentation on using and programming
\textsf{Equalizer}~\cite{Eilemann:13}. In the following related work we assume
these two publications and their references as a starting point, and focus on
the new work published since 2009.

@@

We have presented a significantly improved generic parallel rendering system
over the original publication \cite{EMP:09}. While the original publication
motivated the system design, this publication describes a feature-rich, mature
implementation capable of supporting a wide variety of use cases. We doubled the
support for scalable rendering modes, many of which are presented here for the
first time. We present new runtime adaptations for better load balance and
performance, describe how common optimizations are integrated into the system,
making Equalizer the most generically available scalable rendering system.

@@

With respect to the feature set implemented, we believe that Equalizer now
covers almost any scenario within its scope. For future work, we would like to
integrate new research for better scalability, new network implementations in
particular for modern zero-copy RDMA based transports, as well as extending the
Sequel abstraction layer for ease of use.
